---
title: "bimbo_data_explore2_renjith"
author: "Renjith Madhavan"
date: "June 15, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("ggplot2")
library(dplyr)
library(data.table)
library(feather)
library(ggplot2)
```

# Load Data from the Rdata files saved earlier
```{r}
setwd("D:/r/wd/bimbo")
load("data/rdf/clients.Rdata")
load("data/rdf/products.Rdata")
load("data/rdf/test.Rdata")
load("data/rdf/town_state.Rdata")
load("data/rdf/train.Rdata")
load("data/rdf/train2.Rdata")
load("data/rdf/validate.Rdata")

```


# Basic Data Exploration
```{r}
str(train)
dim(train)
summary(train)
str(clients)
str(products)
str(town_state)
head(products)
```

# using dplyr to summarize data
# Exploring some sample products
```{r}
head(train2)
p1240 <- filter(train2, product == 1240)
filter(products, product == 1240)
dim(p1240)
head(p1240)
mean(p1240$demand)
median(p1240$demand)
summary(p1240$demand)
filter(p1240, demand > 1000)
hist(log(p1240$demand))
summarise(p1240, min_returns = min(returns), max_returns = max(returns), 
          mean_returns = mean(returns), median_returns = median(returns))
summarise(p1240, no_txns=n(),
          total_sales_units=sum(sales_units),
          total_returns_units=sum(returns_units))

p1240 %>%
  filter(demand > 500) %>%
  summarise(num=n())
train2_weekly_sales <- 
train2 %>%
  group_by(week) %>%
  summarise(sales_units=sum(sales_units),
            return_units=sum(returns_units)) %>%
            #return_percent=(sum(sales_units-returns_units)/sum(sales_units)*100)) %>%
  arrange(week)
train2_weekly_sales
```

# Some basic plotting
ggplot(train2_weekly_sales, aes(x = week, y = paste0(round(sales_units/1e6, 2), "$", "M"), col=return_units)) +
  geom_point()

ggplot(train2_weekly_sales, aes(x = week, y = paste0(round(sales_units/1e6, 2), "$", "M"))) +
  geom_point()
#
ggplot(train2_weekly_sales, aes(x = week, y = round(sales_units/1000000,2))) +
  geom_point() + geom_smooth()

  






