---
title: "process data"
author: "Renjith Madhavan"
date: "July 26, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("dplyr")
library(dplyr)
library(data.table)
#library(feather)
library(ggplot2)
#library(treemap)
#library(h2o)
library(sqldf)
library(stringr)
#library(caret)
```

```{r, include=FALSE}
#setwd("/Volumes/Half_Dome/datasets/grupo-bimbo/")
setwd("D:/r/wd/bimbo/data/source")

```

## Process the data to add new features
## Below are the Functions used.
- brand_list function : This function will split extarct the brand name from each product name
- extract_token function : This function will extract a regular expression keyword from the character string(product name)
- extract_weight function : This function will extract weight of the product from the product name vector
- extract_pieces function :  This function will extract number of pieces in a product from the product name

```{r}
brand_list <- function(x) {
  tokens <- strsplit(as.character(x), " ")[[1]]
  tokens[length(tokens) - 1]
}

extract_token <- function(value, expr) {
  tokens <- strsplit(value, " ")
  index <- grep(expr, tokens)
  ifelse(length(index) == 0, NA, tokens[index[1]])
}

extract_weight <- function(product_name) {
  weight_str <- extract_token(product_name, "\\d+[Kg|g]")
  if (is.na(weight_str)) return(NA)
  groups <- str_match_all(weight_str, "(\\d+)(Kg|g)")
  weight <- strtoi(groups[[1]][2])
  unit <- groups[[1]][3]
  ifelse(unit == "Kg", 1000 * weight, weight)
}

extract_pieces <- function(product_name) {
  pieces_str <- extract_token(product_name, "\\d+p\\b")
  if (is.na(pieces_str)) return(NA)
  groups <- str_match_all(pieces_str, "(\\d+)(p)")
  return(strtoi(groups[[1]][2]))
}

```
