---
title: "process data"
author: "Renjith Madhavan"
date: "July 26, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("dplyr")
rm(list=ls())
library(dplyr)
library(data.table)
#library(feather)
library(ggplot2)
#library(treemap)
#library(h2o)
library(sqldf)
library(stringr)
#library(caret)
```

```{r, include=FALSE}
#setwd("/Volumes/Half_Dome/datasets/grupo-bimbo/")
setwd("D:/r/wd/bimbo/data/source")

```

## Process the data to add new features
> Below are the Functions used. 

1. brand_list function
  + This function will split extarct the brand name from each product name
2. extract_token function
  + This function will extract a regular expression keyword from the character string(product name)
3.  extract_weight function
  + This function will extract weight of the product from the product name vector
4.  extract_pieces function
  + This function will extract number of pieces in a product from the product name

```{r}
brand_list <- function(x) {
  tokens <- strsplit(as.character(x), " ")[[1]]
  tokens[length(tokens) - 1]
}

extract_token <- function(value, expr) {
  tokens <- strsplit(value, " ")
  index <- grep(expr, tokens)
  ifelse(length(index) == 0, NA, tokens[index[1]])
}

extract_weight <- function(product_name) {
  weight_str <- extract_token(product_name, "\\d+[Kg|g]")
  if (is.na(weight_str)) return(NA)
  groups <- str_match_all(weight_str, "(\\d+)(Kg|g)")
  weight <- strtoi(groups[[1]][2])
  unit <- groups[[1]][3]
  ifelse(unit == "Kg", 1000 * weight, weight)
}

extract_pieces <- function(product_name) {
  pieces_str <- extract_token(product_name, "\\d+p\\b")
  if (is.na(pieces_str)) return(NA)
  groups <- str_match_all(pieces_str, "(\\d+)(p)")
  return(strtoi(groups[[1]][2]))
}

```

# Load the data

```{r}

load("train.Rdata")
load("test.Rdata")
load("products.Rdata")
load("town_state.Rdata")

```

# extract brand, weight and pieces

```{r}

products$product_name <- as.character(products$product_name)
products$brands <- unlist(lapply(products$product_name, brand_list))

# delete the header
products <- products[-c(products$brands == "IDENTIFICADO"),]

products$weight <- unlist(lapply(products$product_name, extract_weight))
products$pieces <- unlist(lapply(products$product_name, extract_pieces))
products$product_name <- NULL

products[1:10,]
dim(products)

```

# Add the extracted features into the training and test data sets using left join

```{r}

train <-  train %>%
  left_join(products, by="product")

test$product <- as.integer(test$product)

test <-  test %>%
  left_join(products, by="product")


```

# Save Tran and test Data sets

```{r}
save(train, file="trainx.Rdata")
save(test, file="testx.Rdata")



```

