---
title: "Modeling_Renjith"
author: "Renjith Madhavan"
date: "June 18, 2016"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(data.table)
library(feather)
library(ggplot2)
library(treemap)
library(h2o)
```

```{r}
setwd("D:/r/wd/bimbo")
load("data/rdf/train2.Rdata")
load("data/rdf/validate.Rdata")

validate$sales_units <- NULL
validate$sales <- NULL
validate$returns <- NULL
validate$returns_units <- NULL

```

# Persistant Baseline Model

This model assumes that the previous week's demand will persist to the following two weeks. If a product or store id is not found in the training data, then the model will predict that the demand will be the overall average demand.

```{r}
train2_sample
x2 <- train2_sample %>%
  group_by(product,client) %>%
  summarise(avg_demand = mean(demand)) %>%
  arrange(product)
x3 <- train2_sample %>%
  group_by(product) %>%
  summarise(avg_demand = mean(demand)) %>%
  arrange(product)

x4 <- train2_sample %>%
  group_by(client) %>%
  summarise(avg_demand = mean(demand)) %>%
  arrange(client)
x5 <- train2_sample %>%
    summarise(avg_demand = mean(demand))
x5

ret_demand <- function(arg1, arg2) {
  if (train4_sample$arg1 %in% x2$product) {
    if (train4_sample$arg2 %in% x2$client)
  }
}
ret_demand(train2_sample$client, train2_sample$product)
train4_sample <- train2_sample[1:7,]
train4_sample[8:10,] <- train3_sample[1:3,]

train4_sample[,7:11] <- NULL
train4_sample$key <- NULL
train4_sample
eval <- train4_sample$demand
train4_sample$predict <- ret_demand(train4_sample$client, train4_sample$product)

x <- train4_sample$product %in% x2$product
x
x2[x2$product==1120,]
```

## Evaluation

We are using the Root Mean Squared Logarithmic Error, or RMSLE. 

$$\epsilon = \sqrt{\frac{1}{n} \sum_{i=1}^{n} \big(log(p_i + 1)-log(a_i + 1)\big)^2}$$

Where:

$\epsilon$ is the RMSLE value (score)

$n$ is the total number of observations in the data set,

$p_i$ is the prediction of demand

$a_i$ is the actual demand for $i$

$log(x)$ is the natural logarithm of $x$


```{r RMSLE}

sqerror <- (log(validate$prediction + 1) - log(validate$demand + 1))^2
epsilon <- sqrt(sum(sqerror) / length(sqerror))

epsilon
  

```


# Modeling using h2o using gbm
```{r}
#Start an h2o cluster
h2o.init(nthreads=-1, max_mem_size = '7G')



```
